---
title: "Evaluating Importance Levels Across Case Studies"
author: "Meghan Fletcher"
date: "1/31/2022"
output: 
  html_document:
    theme: flatly
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```

# Load data

```{r}
library(here)
source(here("00-load-libraries.R"))
load(here("data","attribs.Rdata")) # from 01-prep-attribute-tables.Rmd
load(here("data","attributes_merged_clean.Rdata"))

```

################################################################################################

# Find Importance Means 
The importance score means of each attribute are reflected in the table. These means are based off of all case studies combined.In order to calculate means, the importance levels needed to converted to numeric value so, _high importance = 3, medium = 2, and low = 1_.

```{r}
# Build a table
merged_importance <- attributes_merged_clean %>% 
  group_by(attribute) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Attribute = attribute,
         Importance = importance) %>% 
  mutate(across(where(is.numeric), ~ round(., 3)))

# Use `kableExtra` package to create table
merged_importance %>% 
  kbl(caption = "Importance Means") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Importance means by dimension

```{r}
# Find means across domains but within each dimension
dimension_importance <- attributes_merged_clean %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list("Mean" = mean, "Standard Deviaton" = sd)) %>% 
  rename(Dimension = dimension) %>% 
  mutate(across(where(is.numeric), ~ round(., 3)))

# Create a table
dimension_importance %>% 
  kbl(caption = "Importance Means by Dimension") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Importance means by domain

```{r}
# Find means across domains but within each dimension
domain_importance <- attributes_merged_clean %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Dimension = dimension,
         Domain = domain,
         Importance = importance) %>% 
  mutate(across(where(is.numeric), ~ round(., 3)))

# Create a table
domain_importance %>% 
  kbl(caption = "Importance Means by Domain") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```



##############################################################################################

# Grouping Importance Stats

## Importance Means by Dimension
```{r}
# Create a table where the average scores of each domain across case studies are represented

# Aguion mean
aguion_dim <- attributes_merged_clean %>% 
  filter(case_study == "Aguion") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Aguion = importance,
         Dimension=dimension) 

# Burden mean
burden_dim <- attributes_merged_clean %>% 
  filter(case_study == "Burden") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Burden = importance) 

# Dickey-Collas mean
dickey_collas_dim <- attributes_merged_clean %>% 
  filter(case_study == "Dickey_Collas") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Dickey_Collas = importance) 

# Eurich mean
eurich_dim <- attributes_merged_clean %>% 
  filter(case_study == "Eurich") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Eurich = importance) 

# Free mean
free_dim <- attributes_merged_clean %>% 
  filter(case_study == "Free") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Free = importance) 

# Friedman mean
friedman_dim <- attributes_merged_clean %>% 
  filter(case_study == "Friedman") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Friedman = importance) 

# Golden mean
golden_dim <- attributes_merged_clean %>% 
  filter(case_study == "Golden") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Golden = importance) 

# Hollowed mean
hollowed_dim <- attributes_merged_clean %>% 
  filter(case_study == "Hollowed") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Hollowed = importance) 

# Kisara mean
kisara_dim <- attributes_merged_clean %>% 
  filter(case_study == "Kisara") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Kisara = importance) 

# Kleisner mean
kleisner_dim <- attributes_merged_clean %>% 
  filter(case_study == "Kleisner") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Kleisner = importance) 

# Lau mean
lau_dim <- attributes_merged_clean %>% 
  filter(case_study == "Lau") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Lau = importance) 

# Mason mean
mason_dim <- attributes_merged_clean %>% 
  filter(case_study == "Mason") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Mason = importance) 

# Mills mean
mills_dim <- attributes_merged_clean %>% 
  filter(case_study == "Mills") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Mills = importance) 

# Pecl mean
pecl_dim <- attributes_merged_clean %>% 
  filter(case_study == "Pecl") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Pecl = importance) 

# Tokunaga mean
tokunaga_dim <- attributes_merged_clean %>% 
  filter(case_study == "Tokunaga") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Tokunaga = importance) 

# Westfall mean
westfall_dim <- attributes_merged_clean %>% 
  filter(case_study == "Westfall") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Westfall = importance) 

# Zhao mean
zhao_dim <- attributes_merged_clean %>% 
  filter(case_study == "Zhao") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Zhao = importance) 
```

```{r}
### Kisara Case Study missing b/c no information forsome of the dimensions 

# Merge all mean datasets together
dimension_importance_merged <- cbind(aguion_dim, burden_dim, dickey_collas_dim, eurich_dim, free_dim, friedman_dim, golden_dim, hollowed_dim,  kleisner_dim, lau_dim, mason_dim, mills_dim, pecl_dim, tokunaga_dim, westfall_dim, zhao_dim) %>% 
  select(Dimension, Aguion, Burden, Dickey_Collas, Eurich, Free, Friedman, Golden, Hollowed, Kleisner, Lau, Mason, Mills, Pecl, Tokunaga, Westfall, Zhao) %>% 
  mutate(across(where(is.numeric), ~ round(., 3)))


# Create a table
dimension_importance_merged %>% 
  kbl(caption = "Importance Means Across by Dimension") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


## Importance Means by Domain

```{r}
# Create a table where the average scores of each domain across case studies are represented

# Aguion mean
aguion_dom <- attributes_merged_clean %>% 
  filter(case_study == "Aguion") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Aguion = importance) 

# Burden mean
burden_dom <- attributes_merged_clean %>% 
  filter(case_study == "Burden") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Burden = importance)

# Dickey-Collas mean
dickey_collas_dom <- attributes_merged_clean %>% 
  filter(case_study == "Dickey_Collas") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Dickey_Collas = importance) 

# Eurich mean
eurich_dom <- attributes_merged_clean %>% 
  filter(case_study == "Eurich") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Eurich = importance)

# Free mean
free_dom <- attributes_merged_clean %>% 
  filter(case_study == "Free") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Free = importance)

# Friedman mean
friedman_dom <- attributes_merged_clean %>% 
  filter(case_study == "Friedman") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Friedman = importance)

# Golden mean
golden_dom <- attributes_merged_clean %>% 
  filter(case_study == "Golden") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Golden = importance)

# Hollowed mean
hollowed_dom <- attributes_merged_clean %>% 
  filter(case_study == "Hollowed") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Hollowed = importance)

# Kisara mean
kisara_dom <- attributes_merged_clean %>% 
  filter(case_study == "Kisara") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Kisara = importance)

# Kleisner mean
kleisner_dom <- attributes_merged_clean %>% 
  filter(case_study == "Kleisner") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Kleisner = importance)

# Lau mean
lau_dom <- attributes_merged_clean %>% 
  filter(case_study == "Lau") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Lau = importance)

# Mason mean
mason_dom <- attributes_merged_clean %>% 
  filter(case_study == "Mason") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Mason = importance)

# Mills mean
mills_dom <- attributes_merged_clean %>% 
  filter(case_study == "Mills") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Mills = importance)

# Pecl mean
pecl_dom <- attributes_merged_clean %>% 
  filter(case_study == "Pecl") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Pecl = importance)

# Tokunaga mean
tokunaga_dom <- attributes_merged_clean %>% 
  filter(case_study == "Tokunaga") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>% 
  rename(Tokunaga = importance)

# Westfall mean
westfall_dom <- attributes_merged_clean %>% 
  filter(case_study == "Westfall") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Westfall = importance)

# Zhao mean
zhao_dom <- attributes_merged_clean %>% 
  filter(case_study == "Zhao") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_importance), list(importance = mean)) %>%  
  rename(Zhao = importance)
```

```{r}
### Kisara Case Study missing b/c no information for some of the dimensions 

# Merge all mean datasets together
means_merged_by_case <- cbind(aguion_dom, burden_dom, dickey_collas_dom, eurich_dom, free_dom, friedman_dom, golden_dom, hollowed_dom,  kleisner_dom, lau_dom, mason_dom, mills_dom, pecl_dom, tokunaga_dom, westfall_dom, zhao_dom) %>% 
  select(dimension...1, domain...2, Aguion, Burden, Dickey_Collas, Eurich, Free, Friedman, Golden, Hollowed, Kleisner, Lau, Mason, Mills, Pecl, Tokunaga, Westfall, Zhao) %>% 
  rename(Dimension = dimension...1, Domain = domain...2) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

# Create a table
means_merged_by_case %>% 
  kbl(caption = "Importance Means Across Case Studies") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

####################################################################################################

# Visualize Importance Means

```{r}
# Create theme
my_theme <-  theme(axis.text.x=element_text(size=7, angle=38, hjust=0.8),
                   axis.text.y=element_text(size=8),
                   legend.text=element_text(size=8),
                   legend.title=element_text(size=9),
                   strip.text=element_text(size=9),
                   # Gridlines
                   panel.grid.major = element_blank(), 
                   panel.grid.minor = element_blank(),
                   panel.background = element_rect(), 
                   axis.line = element_line())
```

```{r}
# Bar graph showing average comparison by dimension across case studies

dimension_comparison <- dimension_importance_merged %>% 
  pivot_longer(!Dimension, names_to = "case_study", values_to = "means") %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))


ggplot(dimension_comparison, aes(x = case_study, y = means, fill = Dimension)) +
  geom_bar(stat="identity", width=0.7, position=position_dodge(width=1)) +
  theme_bw() + my_theme +
  facet_wrap(~Dimension, scales = "free") +
  theme(legend.position="top") +
  scale_fill_brewer(palette = "Accent") +
  geom_hline(data=dimension_importance, aes(yintercept = (Mean)), linetype="dashed", colour="black") +
  labs(x = "Case Studies", y = "Importance Averages")
```

```{r}
# Make a stacked graph for the data

importance_stacked <- ggplot(dimension_comparison, aes(x = case_study, y = means, fill = Dimension, label = means)) +
  geom_bar(stat="identity", position="stack") +
  theme_bw() + my_theme +
  theme(legend.position="top") +
  labs(x = "Case Studies", y = "Importance Averages") +
  scale_fill_brewer(palette = "Accent") +
  geom_text(size = 3, position = position_stack(vjust = 0.5))
plot(importance_stacked)
```


##################################################################################################

# Importance Score Proportions

```{r}
# Create a table that shows the counts and proportions of attribute scores to help identify which are scoring higher than others and vice versa.

importance_stats <- attributes_merged_clean %>% 
  select(dimension, importance) %>% 
  tabyl(dimension,importance) %>%
  adorn_percentages() %>% 
  adorn_pct_formatting(digits = 2) %>% 
  column_to_rownames(var = "dimension")


# Create a table
importance_stats %>% 
  kbl(caption = "Proportion of Importance Levels by Dimension") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```











