---
title: "CRF PCA Analysis"
author: "Meghan Fletcher"
date: "2/15/2022"
output: 
  html_document:
    theme: flatly
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```

# Load data

```{r}
library(here)
source(here("00-load-libraries.R"))
load(here("data","attribs.Rdata")) # from 01-prep-attribute-tables.Rmd
load(here("data","attributes_merged_clean.Rdata"))

```


#####################################################################################################################################

# Prepare initial datasets for PCA Analysis

```{r}
# Make attributes row 1
attributes_clustering <- attributes_merged_clean %>% 
  select(case_study, dimension, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = case_study, values_from = official_score, values_fill = 0) %>% 
  # Rename dimension and domain to be capital
  rename(Dimension = dimension, Domain = domain)
  


# Make case studies row 1
case_clustering <- attributes_merged_clean %>% 
  select(case_study, dimension, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = attribute, values_from = official_score, values_fill = 0)%>% 
  # Rename dimension and domain to be capital
  rename(Dimension = dimension, Domain = domain)
```


# PCA Analysis for all attributes (colored by dimension)


```{r}
# Prep data for PCA analysis
attributes_dimension_pca <- attributes_clustering %>%
  select(c(4:16)) %>% 
  scale() %>% 
  prcomp()


# Create PCA plot
autoplot(attributes_dimension_pca,
         data = attributes_clustering,
         colour = "Dimension",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "black",
         loadings.label.vjust = 1.2,
         loadings.label.hjust = 0.8,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(title = "PCA Analysis of Case Study Attributes (by Dimension)")
```


# PCA Analysis for all attributes (colored by domain)

```{r}
# Prep data for PCA analysis
attributes_domain_pca <- attributes_clustering %>%
  select(c(4:16)) %>% 
  scale() %>% 
  prcomp()


# Create PCA plot
autoplot(attributes_domain_pca,
         data = attributes_clustering,
         colour = "Domain",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "black",
         loadings.label.hjust = 1,
         loadings.label.vjust = 0.5,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(title = "PCA Analysis of Case Study Attributes (by Domain)")
```

##################################################################################################################################


# Breaking the PCA Analyses Down by Dimension

## PCA Analysis for Ecological Dimension (Comparing Case Studies)

```{r}
# prepare data for ecological dimension PCA analysis
ecological_data <- attributes_merged_clean %>% 
  filter(dimension == "Ecological") %>% 
  select(case_study, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = case_study, values_from = official_score, values_fill = 0)%>% 
  # Rename dimension and domain to be capital
  rename(Domain = domain)
```


```{r}
# Prep data for PCA analysis
ecological_pca <- ecological_data %>%
  select(c(3:15)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(ecological_pca,
         data = ecological_data,
         colour = "Domain",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "darkgreen",
         loadings.label.hjust = 1,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, 
                                  linetype="solid", 
                                  colour ="black")) +
  labs(title = "Ecologcial Dimension PCA Analysis (Comparing Case Studies)")
```


## PCA Analysis for Socio-Economic Dimension (Comparing Case Studies)

```{r}
# prepare data for ecological dimension PCA analysis
socio_data <- attributes_merged_clean %>% 
  filter(dimension == "Social-economic") %>% 
  select(case_study, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = case_study, values_from = official_score, values_fill = 0) %>% 
  # Rename dimension and domain to be capital
  rename(Domain = domain)
```


```{r}
# Prep data for PCA analysis
socio_pca <- socio_data %>%
  select(c(3:14)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(socio_pca,
         data = socio_data,
         colour = "Domain",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "navy",
         loadings.label.hjust = 1,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(title = "Socio-Economic Dimension PCA Analysis (Comparing Case Studies)")
```


## PCA Analysis for Governance Dimension (Comparing Case Studies)

```{r}
# prepare data for governance dimension PCA analysis
goverance_data <- attributes_merged_clean %>% 
  filter(dimension == "Goverance") %>% 
  select(case_study, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = case_study, values_from = official_score, values_fill = 0)%>% 
  rename(Domain = domain)
```


```{r}
# Prep data for PCA analysis
goverance_pca <- goverance_data %>%
  select(c(3:14)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(goverance_pca,
         data = goverance_data,
         colour = "Domain",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "purple",
         loadings.label.hjust = -0.2,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(title = "Governance Dimension PCA Analysis (Comparing Case Studies)")
```

#################################################################################################################################


# PCA with Attributes as the lines and cases as the points (Comparing Attributes)

```{r}
# Prep data for PCA analysis
case_pca <- case_clustering %>%
  select(c(4:41)) %>% 
  scale() %>% 
  prcomp()


# Create PCA plot
autoplot(case_pca,
         data = case_clustering,
         colour = "case_study",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "black",
         loadings.label.vjust = 1.2,
         loadings.label.hjust = 0.8) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(colour = "Case Studies", title = "PCA Analysis using Case Studies as Points")
```

## Case Study PCA Analysis of Ecological Dimension (Comparing Attributes)

```{r}
# prepare data for ecological dimension PCA analysis
ecological_data2 <- attributes_merged_clean %>% 
  filter(dimension == "Ecological") %>% 
  select(case_study, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = attribute, values_from = official_score, values_fill = 0)
```

```{r}
# Prep data for PCA analysis
ecological_pca2 <- ecological_data2 %>%
  select(c(2:14)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(ecological_pca2,
         data = ecological_data2,
         colour = "case_study",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "darkgreen",
         loadings.label.vjust = -0.5) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(colour = "Case Studies", title = "Ecologcial Dimension PCA Analysis (Comparing Attributes)")
```


## Case Study PCA Analysis of Socio-Economic Dimension (Comparing Attributes)

```{r}
# prepare data for ecological dimension PCA analysis
socio_data2 <- attributes_merged_clean %>% 
  filter(dimension == "Social-economic") %>% 
  select(case_study, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = attribute, values_from = official_score, values_fill = 0)
```

```{r}
# Prep data for PCA analysis
socio_pca2 <- socio_data2 %>%
  select(c(2:11)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(socio_pca2,
         data = socio_data2,
         colour = "case_study",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "navy") +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(colour = "Case Studies", title = "Socio-Economic Dimension PCA Analysis (Comparing Attributes)")
```


## Case Study PCA Analysis of Socio-Economic Dimension (Comparing Attributes)

```{r}
# prepare data for ecological dimension PCA analysis
goverance_data2 <- attributes_merged_clean %>% 
  filter(dimension == "Goverance") %>% 
  select(case_study,  attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = attribute, values_from = official_score, values_fill = 0)
```

```{r}
# Prep data for PCA analysis
goverance_pca2 <- goverance_data2 %>%
  select(c(2:11)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(goverance_pca2,
         data = goverance_data2,
         colour = "case_study",
         label.size = 4,
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "purple",
         loadings.label.hjust = -1) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(colour = "Case Studies", title = "Governance Dimension PCA Analysis")
```














